Refinement of Thermostated Molecular Dynamics via Backward Error Analysis

### 2018-06-19 rigid_bodies.tex
Inclusion of an method-introducing paragraph in the Discretization section

In Fig.~\ref{fig:properties}, we present some thermodynamic properties computed for the liquid water system using several NVT-MD methods with different time step sizes.
All simulations were carried out by specifying $T = 298.0~\text{K}$ and the analyzed quantities are the estimated temperature $T_\text{est} = \frac{2\langle K \rangle}{(6N-3)k_\mini{B}}$,
the mean potential energy per molecule $\langle U/N \rangle$,
the mean internal virial per molecule $\langle W/N \rangle$, and
the constant-volume specific heat $c_\mini{V} = \frac{\langle \Ham{}^2 \rangle - \langle \Ham{} \rangle^2}{N k_\mini{B} T^2}$.
The internal virial $W$ is computed as described in Ref.~\citenum{Silveira_2017}.
All symbols in Fig.~\ref{fig:properties} represent results obtained after $18~\text{ns}$ of production time, while the lines are just guides for the eyes.
The horizontal, dotted lines are meant to help visualizing the departure of the computed averages from their expected values.
They correspond to the results obtained by employing the Refined NHC method with $\timestep = 1~\text{fs}$.
Error bars were obtained using the Overlapping Batch Means estimator \cite{Meketon_1984, Flegal_2010} and standard uncertainty propagation formulas.

@@

@@

>>>>

In Fig.~\ref{fig:properties}, we present some thermodynamic properties computed for the liquid water system using several NVT-MD methods with different time step sizes.
All simulations were carried out by specifying $T = 298.0~\text{K}$ and the analyzed quantities are the estimated temperature $T_\text{est} = \frac{2\langle K \rangle}{(6N-3)k_\mini{B}}$,
the mean potential energy per molecule $\langle U/N \rangle$,
the mean internal virial per molecule $\langle W/N \rangle$, and
the constant-volume specific heat $c_\mini{V} = \frac{\langle \Ham{}^2 \rangle - \langle \Ham{} \rangle^2}{N k_\mini{B} T^2}$.
The internal virial $W$ is computed as described in Ref.~\citenum{Silveira_2017}.
All symbols in Fig.~\ref{fig:properties} represent results obtained after $18~\text{ns}$ of production time, while the lines are just guides for the eyes.
The horizontal, dotted lines are meant to help visualizing the departure of the computed ensemble averages from their expected values.
They correspond to average results obtained with $\timestep = 1~\text{fs}$ by employing the three refined methods.
Error bars were obtained using the Overlapping Batch Means estimator \cite{Meketon_1984, Flegal_2010} and standard uncertainty propagation formulas.

@@

Fig.~\ref{fig:properties} contains results obtained by using five different NVT integrators.
First, for the sake of comparison, we test our measure-preserving extension to rigid bodies of the method of Martyna \textit{et al}. \cite{Martyna_1996} without doing any refinement, such as detailed in Sec.~\ref{sec:nvt}.
Another method we use with no refinement is that of Kamberaj \textit{et al}. \cite{Kamberaj_2005}.
We will show that, besides the spurious energy flux between the thermostats, such method exhibits some discretization-related issues....................................

@@

SAY THAT BUSSI AND MARTYNA, BOTH WITHOUT REFINEMENT, YIELD SIMILAR RESULTS.
